TR Invariant T.I.

### 2017-04-17 Notes of various papers/TR invariant topological insulators T. Hughes. Dissertation/note.tex
[major] Discuss an edge state at the interface of the 2d dirac model.

>>>>

\subsection{Edge States}
\label{sec:Edge States}
Inspired by lecture by Kane of Topological Insulators (BSS 2016), I
will analyse the continuum limit of this model at the  point
$(p_x=0,p_y=0)$, where the energy $E=0$. I also assume that we have placed
to materials adjacent to each other, on with $m<0$, and the other with
$m>0$. Therefore, at the interface, we could have $m$ as a function of
$x$ such that $m(0)=0$.

At this point $x=0$, $\sin(p_x)\to p_x$ , and is replaced by $-i\hbar
\partial _x$. The Schrodinger equation is H$\psi $=0 After the
calculation, the equation is (with $\hbar=1$):
\begin{equation}
    \left[i\partial_x \sigma^x + i\partial_y \sigma^y +
    m\sigma^z\right] \psi = 0
\end{equation}
However, this coupled PDE is hard to solve. Therefore, I restrict
their value on $x$, and solve the ODE:
\begin{align}
    i\partial_x \psi_2(x) + m\psi_1(x) &= 0 \\
    i\partial_x \psi_1(x) - m\psi_2(x) &= 0
\end{align}
If assuming $m(x)$ is in the form of $m(x)=x$, i.e. positive when
$x>0$, and negative when $x<0$, then the solution is:
\begin{align}
    \psi_1 (x,y) &= e^{\text{Int}(x)} C(y) \\
    \psi_2 (x,y) &= -i \psi_1(x,y)
\end{align}
where $\text{Int}(x)=\int_1^x -m(k)\dd{k}$. $\text{Int}(x)$ has the
property of goes to $-\infty$ as $x\to \pm\infty$.

If, on the contrary, assuming $m(x)$ is in the form of $m(x)=-x$, i.e. positive when $x<0$, and negative when $x>0$, then the solution is:
\begin{align}
    \psi_1 (x,y) &= e^{-\text{Int}(x)} C(y) \\
    \psi_2 (x,y) &= i \psi_1(x,y)
\end{align}
In both cases, the function are exponentially decaying wave in the
interface at $m(0)=0$.
